\bf Title here

### 2020-08-19 paper/paper.Rmd
change the notation for optim constraint

Now we begin to formulate the optimisation problem. Given a randomly generated starting basis $\mathbf{A}_1$, projection pursuit finds the final projection basis $\mathbf{A}_T = [\mathbf{a}_1, \cdots, \mathbf{a}_d]$, where $\mathbf{a}_i \in \mathbb{R}^{p}$, satisfies the following optimisation problem:

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{X} \cdot \mathbf{A}) \\
s.t. &  \langle \mathbf{a}_i, \mathbf{a}_j \rangle = \delta_{ij}, \forall \mathbf{a}_i, \mathbf{a}_j \in \mathbf{A}
\end{align}

Where $\delta_{ij}$ is the kronecker delta that takes 1 if $i = j$ and 0 otherwise.

>>>>

Now we begin to formulate the optimisation problem. Given a randomly generated starting basis $\mathbf{A}_1$, projection pursuit finds the final projection basis $\mathbf{A}_T$ that satisfies the following optimisation problem:

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{X} \cdot \mathbf{A}) \\
&s.t.  \mathbf{A}^{\prime} \mathbf{A} = I_d
\end{align}

where $I_d$ is the d-dimentional identity matrix. The constraint requires the projection basis $\mathbf{A}$ to be a orthonogal matrix with each column vector being orthornormal.

### 2020-08-19 paper/paper.tex
change the notation for optim constraint

Now we begin to formulate the optimisation problem. Given a randomly
generated starting basis \(\mathbf{A}_1\), projection pursuit finds the
final projection basis
\(\mathbf{A}_T = [\mathbf{a}_1, \cdots, \mathbf{a}_d]\), where
\(\mathbf{a}_i \in \mathbb{R}^{p}\), satisfies the following
optimisation problem:

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{X} \cdot \mathbf{A}) \\
s.t. &  \langle \mathbf{a}_i, \mathbf{a}_j \rangle = \delta_{ij}, \forall \mathbf{a}_i, \mathbf{a}_j \in \mathbf{A}
\end{align}

Where \(\delta_{ij}\) is the kronecker delta that takes 1 if \(i = j\)
and 0 otherwise.

>>>>

Now we begin to formulate the optimisation problem. Given a randomly
generated starting basis \(\mathbf{A}_1\), projection pursuit finds the
final projection basis \(\mathbf{A}_T\) that satisfies the following
optimisation problem:

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{X} \cdot \mathbf{A}) \\
&s.t.  \mathbf{A}^{\prime} \mathbf{A} = I_d
\end{align}

where \(I_d\) is the d-dimentional identity matrix. The constraint
requires the projection basis \(\mathbf{A}\) to be a orthonogal matrix
with each column vector being orthornormal.
